Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis

### 2018-07-19 article/article_1.tex
Agregando dados de sharelatex

\title{Illumination Level Independence in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In the literature we can found a work \cite{RIVERA2017144} that show as some speckle indexes
have a frequency filter behavior; by example, we have the $AVD$ \cite{avd} and 
$IM$ \cite{ARIZAGA1999163} index, that they filter
the information like a first order high pass filter with cut-off in the middle
of normalized frequency band. For this reason, It is important analyze how,
the chosen frequency band, alter the result of selected index.
By other side others works 
\textcolor{red}{[cita] (acho tinha um artigo de kefir que tinha problemas de iluminacao)} 
show the problem of
made a speckle analysis with the presence of variation of illumination, because
the most of biospeckle indexes in the literature are influenced in your values
by the use of a determinate illumination level.
Thus, the present work searches establish a relation between the frequency band used
and the speckle index; specifically here will be studied the dependence of
the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.

@@

\subsection{Obtaining data packages in the test over an ink sample}
\label{sec:descriptionink}
The Fig. \ref{fig:system} shows the system diagram of the ink sample test; in It, we can see as
a red laser was pointed to an ink sample, the drying process is monitored by a digital camera;
the images are collected receiving two different illumination levels, because these 
are obtained using a neutral 
density lens between the ink sample and the laser, covering partially the view angle of the laser.
The images in each data package
are sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{System description.}
\label{fig:system}
\end{figure}
In each one of the $11$ packages were selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the figure  we have the
portion of image that was altered by the neutral density lens. The figure represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}. Being this value associated in the literature with
the illumination quantity in the surface of sample \cite{Nothdurft:05}; corresponding thus high values of $\mu$
to places with more illumination. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}

\subsection{Obtaining data packages in the test over a paper piece}
\label{sec:descriptionpaper}
The test over a paper piece has a similar configuration that seen in
the Fig. \ref{fig:system} with the difference that in the paper piece test is not used
the neutral density lens; thus It is collected one data package
sampled with a frequency of $F_s=$\textcolor{red}{[[[12.5]]]} hertz, being 
collected in total $N=129$ images of 640$\times$480 pixels.
The Fig. \ref{fig:meanpaper} represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
illumination level of laser over the paper has a elliptical form being it higher 
in the centroid close to the image top.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall.eps}
\caption{Light intensity distribution in the paper piece test.}
\label{fig:meanpaper}
\end{figure}

@@

\subsection{Data package filtering in three frequency band}
\label{subsec:firfilters}
Each data package or sub package ($P_T$) goes through of a filter bank with 4 outputs  having each
one a different type of processing, the first output is trivial because it
leave pass the information freely, this package is called of $P_T$, the others 3 processing types
return  signals, filter by frequency band; thus, 
we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies); obtaining at end, the packages 
$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
Internally the obtaining of the filtered packages are realized using in cascade
two low pass Finite Impulse Response ($FIR$) filters of order $32$, so that
the sum of signals $P_X+P_Y+P_Z=P_T$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\columnwidth]{firfilters.eps}
\caption{Filtering of data packages.}
\label{fig:firfilters}
\end{figure}

\subsection{Temporal speckle deviation matrix}
\label{subsec:deviation}
The calculus of the temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
uses as input, the $N$ images of a data package.
We designate to each image, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, being $k$ an integer;
thus, to get the value $\sigma$, 
 it is necessary to get 
the matrix $\sigma$ as seen in the Equation \ref{eq:cont2}, 
\begin{equation}\label{eq:cont2}
\sigma  = \sqrt{ \frac{1}{N} \sum_{k=1}^{N} (\mathbf{I}_{k}-\mu)^2  },
\end{equation}
being that, the value $\mu$ can be calculated as, 
\begin{equation}\label{eq:cont1}
\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k},
\end{equation}

Additionally, can be defined the temporal speckle deviation index, $\bar{\sigma}=<\sigma>$, as the mean value
of all elements in $\sigma$, being $<.>$ the mean spatial operator.
%And $\sigma_p$ as any value of an element in  $\sigma$.

\subsection{Datapack processing in the ink drying test }
\label{subsec:numprocink}

As explicated in the Sec. \ref{sec:descriptionink} we have in the ink drying test, analysis regions  with
two levels of illumination in each data packages; thus, we  separate each package in two sub package
(left and right), representing each one the regions shown in the Fig. \ref{fig:regions}.
These sub packages are filtered following the process explicated in the Sec. \ref{subsec:firfilters},
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}
Immediately later of obtained these filtered packages, over each one of these
is calculated the temporal speckle deviation matrix and in base of this result are obtained the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$. The procedure to obtain these values is 
explicated in the Sec. \ref{subsec:deviation}.

\subsection{Statistical analysis of relation between the matrices $\sigma$ and $\mu$}
\label{subsec:statistical}
We define $\sigma_i$ and $\mu_i$
as the values in the $i-th$ position in the $\sigma$  
and $\mu$ matrices, respectively; also define $\mu_p$
as any element value in  $\mu$.
And finally we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
With all these in mint we calculate the vectors $L_p$, $\sigma_p$ and
$e_p$ using all the $\mu_p$ values, according the next description.
\begin{itemize}
 \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  being $L_p(\mu_p)$ the number of elements
 in the set $S_{\mu_p}$ and $card(.)$ the cardinality function operator.
 \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
 the mean value of elements in the set $S_{\mu_p}$ and $mean(.)$ represents the mean value function operator.
 \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
 the standard  deviation value of elements in the set $S_{\mu_p}$ and $std(.)$ represents the standard deviation function operator.
\end{itemize}
In the practice only will be take in count in the vectors, values of $\mu_p$
with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.

\subsection{Datapack processing in the paper piece test }
\label{subsec:numprocink}

As explicated in the Sec. \ref{sec:descriptionpaper}, in this test we have one data package;
this package is filtered following the process explicated in the Sec. \ref{subsec:firfilters},
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$,
over each one of these filtered packages 
are calculated the temporal speckle mean matrix and the 
temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering2.eps}
\caption{Filtering of data package in paper piece test.}
\label{fig:filtering2}
\end{figure}

In base of these results are made statistical analysis to obtain the 
vectors $\sigma_p$, $\mu_p$, $e_p$ to each one of bands. 
The procedure to obtain these values is explicated in the Sec. \ref{subsec:statistical}.

@@

\subsection{Numerical results in the ink drying test} 
\label{subsec:numericalink}
In the Fig. \ref{fig:numerical} we can see the result of data packages processing 
 in the ink drying test. The Fig. \ref{fig:allink}
represent the $\bar{\sigma}_T$ value in two light intensity levels, It is calculates over the package $P_T$
trough the time, and use the complete frequency band.
The Fig. \ref{fig:stdxink}
represent the $\bar{\sigma}_X$ value in two light intensity levels, It is calculates over the package $P_X$
trough the time, and use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
The Fig. \ref{fig:stdyink}
represent the $\bar{\sigma}_Y$ value in two light intensity levels, It is calculates over the package $P_Y$
trough the time, and use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
And the Fig. \ref{fig:stdzink}
represent the $\bar{\sigma}_Z$ value in two light intensity levels, It is calculates over the package $P_Z$
trough the time, and use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-all.eps}
	\caption{$\bar{\sigma}_T$ value through  the time.}
        \label{fig:allink}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandx.eps}
	\caption{$\bar{\sigma}_X$ value through  the time.}
        \label{fig:stdxink}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandy.eps}
	\caption{$\bar{\sigma}_Y$ value through  the time.}
        \label{fig:stdyink}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandz.eps}
	\caption{$\bar{\sigma}_Z$ value through  the time.}
        \label{fig:stdzink}
    \end{subfigure}

\caption{Numerical results in the ink drying test.}\label{fig:numerical}
\end{figure}
As can be seen, when analyze the index over the complete frequency band (Fig. \ref{fig:allink}),
we have different results to both illuminations levels, being that the index
value It is major in the left side,that is the side with most illumination. This 
indicates a positive influence of illumination level in the index value.
By other side, if we observe the figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink},
we can perceive as the index values from different
illuminations  turn most similar with the grow of frequency.
being greater this similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
Thus the similarity is limit by the sampling frequency used.

Finally It is important highlight that in an ink drying test, like the used here,
It is characterized by speckle signals with high frequencies in the begin time
of drying and  speckle signals with low frequencies at end, being gradual this frequency transition
until reach the limit of signal and to have only the noise of test.
So that, when in the figures It is observe a horizontal line in the index, these data
should not be use in the comparisons, even if they are similar, given that these
only are show the noise of test. By example, in the Fig. \ref{fig:stdzink}
we filter so that only have high frequency signals; later, we know that these only happen
in the begin of drying process, and in the figure this happen from 0 until
the 50 minutes and later only have a similar horizontal line in both illuminations.
This indicates that the comparisons of index illumination independence
only should be made between these minutes because out this range we will be using
the noise of test in the comparisons.

\subsection{Numerical results in the paper piece test} 
\label{subsec:numericalpaper}
In the Fig. \ref{fig:papelstd} we can see the result of the processing 
the data packages in the paper piece test. The Fig. \ref{fig:papelall}
represent the $\sigma_T$ matrix that use the complete frequency band.
The Fig. \ref{fig:papelstd_stdx}
represent the $\sigma_X$ matrix that use the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
The Fig. \ref{fig:papelstd_stdy}
represent the $\sigma_Y$ matrix that use the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
And the Fig. \ref{fig:papelstd_stdz} 
represent the $\sigma_Z$ matrix that use the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.485\textwidth}
        \includegraphics[width=\textwidth]{stdall.eps}
	\caption{$\sigma_T$ matrix over the complete frequency band.}
        \label{fig:papelall}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.465\textwidth}
        \includegraphics[width=\textwidth]{stdx.eps}
	\caption{$\sigma_X$ matrix over the inferior third of the frequency band.}
        \label{fig:papelstd_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy.eps}
	\caption{$\sigma_Y$ matrix over the middle third of the frequency band.}
        \label{fig:papelstd_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz.eps}
	\caption{$\sigma_Z$ matrix over the superior third of the frequency band.}
        \label{fig:papelstd_stdz}
    \end{subfigure}

@@

In the next group of graphics we analysis the relation between a value $\sigma_p$,
in the $\sigma$ matrix, with a value $\mu_p$, in the $\mu$ matrix, to all
frequency bands. 
These analysis have importance because  the value $\mu_p$
is related with the illumination level in the surface of sample \cite{Nothdurft:05}
and the color or material of sample. Thus, when we choose $\mu_p$  as reference variable
in a homogeneous sample,  
in true we choose indirectly the illumination level in the surface.
In these sense, the Figs. \ref{fig:papelilllevel}, \ref{fig:illlevel_stdx}, \ref{fig:illlevel_stdy}
and \ref{fig:illlevel_stdz} show the variables $\sigma_p$, $e_p$ and $L_p$ in function
of  $\mu_p$, to the case of the complete frequency band, the inferior third of the frequency band,
the middle third of the frequency band and the superior third of the frequency band,
respectively in each sub figure. It is import to note that $e_p$ ever is graph as percentage
in the relation to the value $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdall_curve.eps}
	\caption{Analysis in the complete frequency band.}
        \label{fig:illlevel_all}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdx_curve.eps}
	\caption{Analysis in the inferior third of the frequency band.}
        \label{fig:illlevel_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy_curve.eps}
	\caption{Analysis in the middle third of the frequency band.}
        \label{fig:illlevel_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz_curve.eps}
	\caption{Analysis in the superior third of the frequency band.}
        \label{fig:illlevel_stdz}
    \end{subfigure}

>>>>

\title{Towards Illumination Level Independence in the Dynamic Laser Speckle Analysis}
%\tnotetext[mytitlenote]{Fully documented templates are available in the 
%elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Dynamic laser speckle is a phenomenon that is used to monitor changes in illuminated samples, and it can be measured by multiple indexes \cite{BSLTLBOOK}. The indexes are associated to the level of changes and could be expressed by numerical and or graphical outcomes that can be affected by filtering action during the image processing \cite{RIVERA2017144}. As an example, we have  the $AVD$ \cite{avd} and 
$IM$ \cite{ARIZAGA1999163} indexes, that filter
the information present in the history of the speckle images like a first order high pass filter with a cut-off in the middle
of the normalized frequency band. 
For this reason, it is important to analyze how
the chosen frequency band alters the result of selected index.
By other side, there is still a limitation to make  speckle analysis in the presence of in-homogeneity of illumination, because
the most of biospeckle indexes are influenced in their values
by the use of a illumination level \cite{REIS2016}.
The illumination level can vary regarding the profile of the sample, such as an apple \cite{KAZ:12a} or a very irregular surface present in a kefir \cite{kefir}. 
It can also vary in accordance with the moisture present in the seed \cite{CARDOSO2011} due to the penetration of the light in the sample, or even when the color of the sample vary such as in the interface of cancer and normal tissues \cite{BCB+:12a}. And that is the reason to a continuous search for an adequate index, despite the fact there are many of them present in literature \cite{BSLTLBOOK}, but still without a solution to the independence of light intensity. 
The movement toward the portable equipment \cite{Bra:17}, reinforce the need to search the methods and its relation with the illumination. 
Thus, the present work aimed to establish a relation between the frequency band used
and the speckle index; particularly in the dependence of
the temporal speckle deviation matrix \cite{Nothdurft:05} with the illumination level.

@@

\subsection{Data packages of drying ink}
\label{sec:descriptionink}
Fig. \ref{fig:system} shows the system setup of the ink sample test during drying where
a red laser was pointed to a layer of drying ink monitored by a digital camera;
the images are collected receiving two different illumination levels, because of the neutral 
density lens covering partially the laser beam \cite{REIS2016}.
The images were placed in data packages
are sampled with a time rate acquisition of $F_s=$ 12.5 hertz, being 
collected $N=400$ images by package. In total were collected $11$ packages 
(with the two different illumination levels each one) at the minutes 
$0$, $10$, $20$, $30$, $40$, $50$, $60$, $75$,$105$,$120$ and $150$ of drying process. 
\begin{figure}[ht!]
\centering
\includegraphics[width=0.65\columnwidth]{system.eps}
\caption{Experimental configuration of dynamic laser speckle formation monitored by digital system with the levels of illumination over a layer of drying ink.}
\label{fig:system}
\end{figure}
In each image of the packages was selected two regions, of $250\times200$ pixels, 
corresponding to the regions with two different illumination levels, 
as shown with black lines in the Fig. \ref{fig:regions}. In the right side of the \ref{fig:regions}  we have the
portion of image that was altered by the neutral density lens. The figure represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}. Being this value associated in the literature with
the illumination quantity in the surface of sample \cite{Nothdurft:05}; corresponding thus high values of $\mu$
to places with more illumination. 
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall_points_all.eps}
\caption{Selected regions and light intensity distribution in the ink drying test.}
\label{fig:regions}
\end{figure}
\textcolor{red}{Nesta figura 2 poderíamos colocar também as imagens cruas dos padrões de speckle}\\

\subsection{Data packages of a steady state paper}
\label{sec:descriptionpaper}
The test over a steady state paper has a similar configuration that seen in
the Fig. \ref{fig:system} with the the absence of 
the neutral density lens. The phenomenon observed was the noise associated to the experimental configuration linked to the camera, to the resolution of the images and also the mechanical noise, and it was collected one data package
sampled with a frequency of $F_s=$ 10 hertz, being 
collected in total $N=129$ images of 640$\times$480 pixels.
The Fig. \ref{fig:meanpaper} represents
with a color bar the result of  calculus the temporal speckle mean matrix ($\mu$) according the Eq. (\ref{eq:cont1})
showed in the Sec. \ref{subsec:deviation}; thus, it is easy to see how the
illumination level of laser over the paper has an elliptical form being highest 
close to the top of the image.
\begin{figure}[h!]
\centering
\includegraphics[width=0.85\columnwidth]{meanall.eps}
\caption{Light intensity distribution in the paper piece test with highest illumination presented by red pixels and lowest by blue pixels.}
\label{fig:meanpaper}
\end{figure}

@@

\subsection{Data package filtering in three frequency band}
\label{subsec:firfilters}
Each data package or sub package ($P_T$) went through of a filter bank with 4 outputs  having each
one a different type of processing, the first output is trivial because it
lets to pass the information freely, this package is called of $P_T$, whilst the other 3 outcomes
return  signals filtered by a frequency band; thus, 
we have the band between $[0,\frac{1}{3}]\frac{F_s}{2}$ (low frequencies),
the band between $[\frac{1}{3},\frac{2}{3}]\frac{F_s}{2}$ (intermediate frequencies) and
the band between $[\frac{2}{3},1]\frac{F_s}{2}$ (high frequencies); obtaining at end, the packages 
$P_X$, $P_Y$ and $P_Z$, respectively; as can be seen in the  Fig. \ref{fig:firfilters}.
The filtered packages of images were carried out using cascades
of two low-pass Finite Impulse Response ($FIR$) filters of order $32$, so that
the sum of signals $P_X+P_Y+P_Z=P_T$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\columnwidth]{firfilters.eps}
\caption{Filtering of data packages.}
\label{fig:firfilters}
\end{figure}

\subsection{Temporal speckle deviation matrix}
\label{subsec:deviation}
The temporal speckle deviation matrix ($\sigma$) \cite{Nothdurft:05} 
used to compare the results was obtained from the $N$ images of a data package.
We designate to each image, in the package $P$, as $\mathbf{I}_{k}$, $1\leq k \leq N$, being $k$ an integer;
thus, to get the value $\sigma$, 
 it is necessary to get 
the matrix $\sigma$ as seen in the Equation \ref{eq:cont2}, 
\begin{equation}\label{eq:cont2}
\sigma  = \sqrt{ \frac{1}{N} \sum_{k=1}^{N} (\mathbf{I}_{k}-\mu)^2  },
\end{equation}
being that, the value $\mu$ can be calculated as, 
\begin{equation}\label{eq:cont1}
\mu =  \frac{1}{N} \sum_{k=1}^{N} \mathbf{I}_{k},
\end{equation}

Additionally, the temporal speckle deviation index can be defined as $\bar{\sigma}=<\sigma>$, the mean value
of all elements in $\sigma$, being $<.>$ the mean spatial operator.
%And $\sigma_p$ as any value of an element in  $\sigma$.

\subsection{Datapack processing in the test of a drying ink}
\label{subsec:numprocink}

We have in the drying ink regions  with
two levels of illumination; thus, we  separated each package in two sub package
(left and right), representing each one of the regions shown in the Fig. \ref{fig:regions}.
These sub-packages were filtered,
obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, that was used to obtain
\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering.eps}
\caption{Filtering of data packages.}
\label{fig:filtering}
\end{figure}

the temporal speckle deviation matrix and the 
temporal speckle deviation indexes $\bar{\sigma}_T$, $\bar{\sigma}_X$, $\bar{\sigma}_Y$ and
$\bar{\sigma}_Z$.

\subsection{Statistical analysis of relation between the matrices $\sigma$ and $\mu$}
\label{subsec:statistical}
We defined $\sigma_i$ and $\mu_i$
as the values in the $i-th$ position in the $\sigma$  
and $\mu$ matrices, respectively; we also defined $\mu_p$
as any element value in  $\mu$.
And we define the set $S_{\mu_p}=\{\sigma_i: \mu_i\equiv \mu_p; \forall i\}$
as the set of all $\sigma_i$  values given that $\mu_i\equiv\mu_p$.
Then, we obtained the vectors $L_p$, $\sigma_p$ and
$e_p$ using all the $\mu_p$ values, according to:
\begin{itemize}
 \item $L_p(\mu_p)=card\left(S_{\mu_p}\right)$,  being $L_p(\mu_p)$ the number of elements
 in the set $S_{\mu_p}$ and $card(.)$ the cardinality function operator.
 \item $\sigma_p(\mu_p)=mean\left(S_{\mu_p}\right)$, being $\sigma_p(\mu_p)$
 the mean value of elements in the set $S_{\mu_p}$ with $mean(.)$ representing the mean value function operator.
 \item $e_p(\mu_p)=std\left(S_{\mu_p}\right)$, being $\e_p(\mu_p)$
 the standard  deviation value of elements in the set $S_{\mu_p}$ with $std(.)$ representing the standard deviation function operator.
\end{itemize}
In practice only will be taken the vectors, values of $\mu_p$
with a $L_p(\mu_p)>200$ samples, to establish a limit to consider a set of representative samples.

\subsection{Datapack processing in the test of a steady state paper}
\label{subsec:numprocink}

In this test we have one data package that was filtered (\ref{fig:filtering2}) obtaining the packages $P_T$, $P_X$, $P_Y$ and $P_Z$, where the outcomes are the temporal speckle mean matrix and the 
temporal speckle deviation matrix, as can be seen in the Fig. \ref{fig:filtering2}.

\begin{figure}[h!]
\centering
\includegraphics[width=0.65\columnwidth]{filtering2.eps}
\caption{Filtering of data package in the steady paper obtaining the mean and the deviation outcomes.}
\label{fig:filtering2}
\end{figure}

@@

\subsection{Numerical results o the drying ink test} 
\label{subsec:numericalink}
In the Fig. \ref{fig:numerical}, we can see the result of processing 
 the drying ink test under the dynamic laser speckle index (DLSI) in two areas with different level of illumination. The Fig. \ref{fig:allink}
represents the $\bar{\sigma}_T$ value in two light intensity levels, and it is done using the package $P_T$
trough the time, with the complete frequency bands.
The Fig. \ref{fig:stdxink}
represents the $\bar{\sigma}_X$ value in two light intensity levels, an it is done using the package $P_X$
trough the time, with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
The Fig. \ref{fig:stdyink}
represents the $\bar{\sigma}_Y$ value in two light intensity levels, and it is done using the package $P_Y$
trough the time, with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz.
And the Fig. \ref{fig:stdzink}
represent the $\bar{\sigma}_Z$ value in two light intensity levels, and it is done using the package $P_Z$
trough the time, with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-all.eps}
	\caption{$\bar{\sigma}_T$ value through  the time.}
        \label{fig:allink}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandx.eps}
	\caption{$\bar{\sigma}_X$ value through  the time.}
        \label{fig:stdxink}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandy.eps}
	\caption{$\bar{\sigma}_Y$ value through  the time.}
        \label{fig:stdyink}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{std-bandz.eps}
	\caption{$\bar{\sigma}_Z$ value through  the time.}
        \label{fig:stdzink}
    \end{subfigure}

\caption{Numerical results in the ink drying test.}\label{fig:numerical}
\end{figure}
As can be seen, when we analyzed the index over the complete frequency band (Fig. \ref{fig:allink}),
we had different results to both illuminations levels, being high in the left side,that is the side with most illumination. This 
indicates a positive influence of illumination level in the index value.
By other side, if we observe the Figures \ref{fig:stdxink}, \ref{fig:stdyink} and \ref{fig:stdzink}
we can see how the index values from different
illuminations  was similar to the frequency level,
being greatest similarity in the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
Thus the similarity is limited by the sampling rate used.

Finally, it is important to highlight that in the drying ink test, the information from the dynamic laser speckle is linked to high frequencies in the beginning of the drying process and  speckle signals with low frequencies at end, being gradual the transition
until reach the lowest level of signal with only the noise of test.
In Figure \ref{fig:numerical} ($c-d$) one can see that after 50 minutes there is a transition of state with the stabilization of the DLSI. Thus, after this point, one has only the inner noise of the system influencing the DLSI.

This indicates that the comparisons of index illumination independence
only should be made between the first minutes because out this range we will be using high contribution of 
the noise as outcome.

\subsection{Numerical results of a steady paper under laser light} 
\label{subsec:numericalpaper}
In the Fig. \ref{fig:papelstd} we can see the result of data processing from the steady
 paper under dynamic laser speckle phenomenon considering an homogeneous illumination and using the standard deviation $\sigma$ as a dynamic laser speckle index (DLSI). Fig. \ref{fig:papelall}
represents the $\sigma_T$ matrix with the complete frequency band, while Fig. \ref{fig:papelstd_stdx}
represents the $\sigma_X$ matrix with the frequency band between $0$ and $\frac{1}{3}\frac{F_s}{2}$Hz.
Fig. \ref{fig:papelstd_stdy} represents the $\sigma_Y$ matrix with the frequency band between $\frac{1}{3}\frac{F_s}{2}$ and $\frac{2}{3}\frac{F_s}{2}$ Hz, and Fig. \ref{fig:papelstd_stdz} 
represents the $\sigma_Z$ matrix with the frequency band between $\frac{2}{3}\frac{F_s}{2}$ and $\frac{F_s}{2}$ Hz.
\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.485\textwidth}
        \includegraphics[width=\textwidth]{stdall.eps}
	\caption{$\sigma_T$ matrix over the complete frequency band.}
        \label{fig:papelall}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.465\textwidth}
        \includegraphics[width=\textwidth]{stdx.eps}
	\caption{$\sigma_X$ matrix over the inferior third of the frequency band.}
        \label{fig:papelstd_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy.eps}
	\caption{$\sigma_Y$ matrix over the middle third of the frequency band.}
        \label{fig:papelstd_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz.eps}
	\caption{$\sigma_Z$ matrix over the superior third of the frequency band.}
        \label{fig:papelstd_stdz}
    \end{subfigure}

@@

In Figure \ref{fig:papelilllevel} we present the relation between an average value of $\sigma_p$,
in the $\sigma$ matrix, with a value $\mu_p$ (mean value representing the illumination level) of the $\mu$ matrix, to all frequency bands, the value $\mu_p$
is related to the illumination level in the surface of the sample \cite{Nothdurft:05}
and the color or material of sample. Thus, when we choose $\mu_p$  as reference 
in a homogeneous sample,  
in true we choose indirectly the illumination level in the surface.
Therefore, Fig. \ref{fig:papelilllevel} shows the variables $\sigma_p$, $e_p$ and $L_p$ in function
of  $\mu_p$, to the case of the complete frequency band (\ref{fig:illlevel_all}), the inferior third of the frequency band (\ref{fig:illlevel_stdx}),
the middle third of the frequency band (\ref{fig:illlevel_stdy}) and the superior third of the frequency band (\ref{fig:illlevel_stdz}). It is import to note that $e_p$ was plot as a relation of $\sigma_p$, this means  $100 \frac{e_p}{\sigma_p} \%$.

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdall_curve.eps}
	\caption{Analysis in the complete frequency band.}
        \label{fig:illlevel_all}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdx_curve.eps}
	\caption{Analysis in the inferior third of the frequency band.}
        \label{fig:illlevel_stdx}
    \end{subfigure}
    ~\\ 
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdy_curve.eps}
	\caption{Analysis in the middle third of the frequency band.}
        \label{fig:illlevel_stdy}
    \end{subfigure}
  ~
    \begin{subfigure}[b]{0.475\textwidth}
        \includegraphics[width=\textwidth]{stdz_curve.eps}
	\caption{Analysis in the superior third of the frequency band.}
        \label{fig:illlevel_stdz}
    \end{subfigure}

    \caption{Relation between the standard deviation value and the illumination level in a steady paper under laser illumination.}
    \label{fig:papelilllevel}
\end{figure}
